\headingfont UNIVERSIDAD DE EXTREMADURA\\ FACULTAD DE CIENCIAS\\[1.5cm] \textbf{ Grado en Física\\ TRABAJO DE FIN DE GRADO\\[3.5cm]} {\setstretch{1.25}\flushleft{\large{\textbf{Developement of a FIWARE-based application for tree species monitoring (dendrometry)}}\\[3.5cm]}}

### 2020-07-03 docs/LaTex/Paper.tex
Fixes cover page

\title{\headingfont%
  UNIVERSIDAD DE EXTREMADURA\\
  FACULTAD DE CIENCIAS\\[1cm]
  \textbf{%
  	Grado en Física\\
    TRABAJO DE FIN DE GRADO\\[3cm]
    \flushleft{\large{Developement of a FIWARE-based application for tree species monitoring (dendrometry)}}\\[3cm]
    %\flushleft{\large{About implementation of LoRa-based wireless monitoring systems for tree species dendrometry.}}\\[3cm]
  }
}

>>>>

\title{\headingfont%
  UNIVERSIDAD DE EXTREMADURA\\
  FACULTAD DE CIENCIAS\\[1.5cm]
  \textbf{%
  	Grado en Física\\
    TRABAJO DE FIN DE GRADO\\[3.5cm]}
    {\setstretch{1.25}\flushleft{\large{\textbf{Developement of a FIWARE-based application for tree species monitoring (dendrometry)}}\\[3.5cm]}}
}
